outline!

### 2016-05-23 paper.tex
update paper
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\documentclass[10pt,twocolumn]{article}
\usepackage{times}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{subcaption}
\usepackage{graphicx,grffile}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usepackage[latin1]{inputenc}

@@

\subsection{Hardware and Software}

In this section we have demonstrated that a design based on an N:1 addressing
scheme that stores both log entries and metadata in the bytestream can provide
the best overall performance, and it does so by a large margin. However, this
process of design we have outlined may not yield such clear cut results when
applied in other contexts that may differ by network and hardware capabilities
as well as configuration options and software versions.

@@

explain that the state space is large, this is hard for humans.
configuration, software versions, hardware versions, interface selections, and
future features.

@@

Describe big picture as if we are going to introduce something like bloom for
describing everything.

], Bloom is purely declarative: the syntax of a program contains the full
spec- ification of its semantics, and there is no need for the programmer to
understand or reason about the behavior of the evaluation engine. Bloom is
based on a formal temporal logic called Dedalu

We use a subset of bloom as a basis for defining interface.

Although we have not chosen to use the most powerful parts of the bloom (eg
task coordination and consistency)
language we have chosen to start with a powerful abstraction because we plan
to take this to 11 (see future work).

\section{Other Interfaces}

>>>>

\documentclass[10pt,twocolumn]{article}
\usepackage{times}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{subcaption}
\usepackage{graphicx,grffile}
\usepackage{pgf}
\usepackage{tikz}
\usepackage{listings}
\usepackage{color}
\usetikzlibrary{arrows,automata}
%\usepackage[latin1]{inputenc}

\lstset{frame=tb,
  language=Ruby,
  captionpos=b,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\scriptsize\ttfamily},
  numbers=none,
  %numberstyle=\tiny\color{gray},
  %keywordstyle=\color{blue},
  %commentstyle=\color{dkgreen},
  %stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

@@

In this section we have demonstrated that a design based on an N:1 addressing
scheme that stores both log entries and metadata in the bytestream can provide
the best overall performance, and it does so by a large margin. However, this
process of design we have outlined may not yield such clear cut results when
applied in a different context.

@@

In practice the real world state space is much larger than the one described
in this section. Ceph alone has hundreds of configuration options, significant
features becoming available with releases each year, and is designed to run on
a wide variety of COTS hardware as well as new NVMe devices, all of which
contribute to a large and dynamic state space. Application-level designs
also contribute to an expanded design space. In the N:1 design of mapping
CORFU onto Ceph the potential amount of I/O parallelism is controlled by 
the value N, however if this value becomes too large there may be no benefit
or performance could suffer from reduced data locality. Other aspects of
application-level design are even more flexible. A wide variety of data
structures could be serialized into the byte stream to handle metadata
management tasks, but selecting a single external index that performs well
across workloads and hardware may not be possible.

Next we present a declarative programming model that seeks to solve the issue
of selecting an optimal mapping between application requirements and object
class implementation.

@@

Ceph is turning into a target for building distrubted services, bringing
distributed programming into the hands of many new people that may have
worked on the periphery of ceph.

Getting consistency and coordination correct is a challenge And as we have seen
optimization at a low-level given a simple set of semantics can yield a large
state space from which to draw designs Difficulty and challenges of writing
distributed software.  Programming distributed systems and applications.

We draw upon the recent work of Bloom a declarative lang thing

BLL (a.k.a. BRADOS) is a declarative language with relational (or tabular)
semantics for RADOS objects, which corresponds to a subset of the BLOOM
language (leaving out temporal logic). BLL borrows from BLOOM the table and
interface collections, the instantaneous implication (‘<=’) operator, as well
as all the collection operators.

BRADOS models the storage system state uniformly as a collection of relations.
The composition of a collection of existing interfaces is then expressed as a
collection of high-level \emph{queries} that describe how a stream of requests
(API calls) are filtered, transformed and combined with existing state to
define streams of outputs (API call returns as well as updates to system
state).  Separating the relational semantics of such compositions from details
of their physical implementations introduces a number of degrees of freedom,
similar to the ``data independence’’ offered by database query languages.  The
choice of access methods (for example, whether to use a bytestream interface or
a key/value store), storage decide classes(e.g., whether to use HDDs or SDDs),
physical layout details (e.g. a 1:1 or 1:N mapping) and execution plans (e.g.
operator ordering) can be postponed to execution time.  The optimal choices for
these physical design details are likely to change much more often than the
logical specification, freeing the interface designer from the need to rewrite
systems and device and interface characteristics change.

\subsection{The CORFU Interface in Bloom}

Listing~\ref{lab} shows code.

\begin{lstlisting}[caption={Hello}, label=lab]
class Corfu
include Bud

state do
table :epoch, [:epoch]
table :log, [:pos] => [:state, :data]

scratch :valid_op, [:type, :pos, :epoch] => [:data]
scratch :invalid_op, [:type, :pos, :epoch] => [:data]

interface input, :op, [:type, :pos, :epoch] => [:data]
interface output, :ret, [:type, :pos, :epoch] => [:retval]
end
\end{lstlisting}

\subsection{Optimzer}

\subsection{Other Interfaces}
